Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-07-20 Paper/intro.tex
..

>>>>

% Outline
1. Significance of the H2/O2 reaction. Include the mechanism and a discussion on why
   is it important to study the kinetics? 
2. Literature survey of studies aimed at quantifying the uncertainty associated with
reaction kinetics (including my own work) and specifically for the H2/O2 reaction.
3. Focus of this work and associated challenges (include a table).
4. Key contributions.
5. Organization
